Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints

### 2017-09-28 2017/ParOptBook/Chapter4.tex
parOptBook: update chapter 4

\begin{lemma}
  on the feasibility of any limit point). Assume the conditions of Theorem \ref{th4:convergence_par} to be met. Then any limit point $\overline x$ of the sequence $\{x_k\}$ is feasible, i.e.,
  \begin{equation}
    \nu(\overline x)=m+1
  \end{equation}
\end{lemma}

\begin{proof}
  Let us assume the opposite. According to (4.55) and (4.56),
\end{proof}

>>>>

\begin{lemma}
  on the feasibility of any limit point). Assume the conditions of Theorem \ref{th4:convergence_par} to be met. Then any limit point $\overline x$ of the sequence $\{x_k\}$ is feasible, i.e.,
  \begin{equation}
    \label{eq4:68}
    \nu(\overline x)=m+1
  \end{equation}
\end{lemma}

\begin{proof}
  Let us assume the opposite. According to (4.55) and (4.56),
  \begin{displaymath}
    \overline x = \lim_{s\to\infty}x_{t-1}=\lim_{s\to\infty}x_t, t=t(x^s).
  \end{displaymath}
  where q s is from (4.57) Therefore, it follows from the assumption $x\in Q$ that there exists such large number $S>1$ and such small subinterval
  \begin{equation}
    \label{eq4:69}
    (u,w)\subset[a,b]\setminus Q,
  \end{equation}
  that
  \begin{equation}
    [x_{t-1},x_t]\subset(u,w),\:t=t(q^s),\:s\ge S.
  \end{equation}

  Let us assign to $Q_j, 1\le j\le m$, from (4.30) their open complements $D_j=[a,b]\setminus Q_j$ consisting of finite number of the open intervals with the positive length (as a consequence of the first condition of Theorem \ref{th4:convergence_par}). For these complements
  \begin{equation}
    g_j(x)>0,x\in D_j,\:1\le j\le m.
  \end{equation}

  It follows from \eqref{eq4:69} that there exist such subsets of indices $M,N\subset\{1,2,\dots,m\}$ that
  \begin{equation}
    (u,\overline x]\subset \cap_{j\in M}D_j,\:[\overline x,w)\subset \cap_{j\in N},
  \end{equation}
  where $(u,w)$ is an open interval from \eqref{eq4:69}.

  According to the trial execution rules and to conditions (4.35) and (4.72), for any interval from (4.70) the relations
  \begin{displaymath}
    \omega_1=\nu(x_{t-1})\in M,\: \omega_2=\nu(x_t)\in N,\:t=t(q^s),
  \end{displaymath}
  hold where $1\le \omega_1,\: \omega_2\le m$. Moreover, according to the rules (4.39) and (4.40) defining the constraints’ check order at trial points,
  \begin{displaymath}
    \nu(x_{t-1}),\:\nu(x_t)\in\{\omega_1,\omega2\},\: t=t(q^{p+1}).
  \end{displaymath}
  In other words, for sufficiently large number $s>1$ the indices assigned to the boundary points of the considered system of intervals $[x_{t-1},x_t],\: t=t(q^s ): s\ge S$ can take the values from the set $\{\omega_1,\omega2\}$ only.

  Now, from (4.46), (4.74), and (4.57) one can conclude that if the point $x$ is not a feasible one, it cannot be a limit point of the sequence $\{x^k\}$, i.e., for any limit point $x$ the condition \eqref{eq4:68} is true.
\end{proof}

\begin{proof} (of Theorem \ref{th4:convergence_par}).

\end{proof}
